\documentclass[11pt, letterpaper]{article}

\begin{document}

\section{Notation}
\subsection{Inputs}

$M_{ot}$: The raw pose of the head marker in the Optitrack frame at time $t$.

$M_c$: The marker pose in the camera frame. Also the offset from the camera to the marker expressed in the camera frame. Note that camera frame = Gazebo frame with a translational offset.

$C_g$: The initial user camera pose in Gazebo coordinates.

$R^o_g$: Rotation component from Gazebo frame to Optitrack frame.

\subsection{Calculated variables}

$M_{oi}$: The initial pose of the marker in the Optitrack frame. "Initial" means the state of the marker pose right before the timestep when the user unpauses motion capture.

$M_{od}$: The desired pose of the marker in the Optitrack frame. This is the raw marker pose while motion capture is enabled.

$M_{gi}$: The initial pose of the marker in the Gazebo frame.

$M_{gd}$: The desired pose of the marker in the Gazebo frame.

$C_{oi}$: The initial pose of the camera in the Optitrack frame.

$C_{od}$: The desired pose of the camera in the Optitrack frame.

$C_{gi}$: The initial pose of the camera in the Gazebo frame. Note that we want $C_g = C_{gi}$.

$C_{gd}$: The desired pose of the camera in the Gazebo frame.

\section{Calculations}
\subsection{Paused}
Calculations at time $t$ when motion tracking is paused:

\[M_{oi} = M_{ot}\]
\[C_{oi} = M_{ot} - (M_c + R^o_g)\]

We can rotate $C_{oi}$ into the Gazebo frame, but we still don't know what the translation is to enforce that $C_{gi}$ is the input user camera pose.

Calculate $T^o_g$, the translation from Gazebo to Optitrack frame, and store it.

\[C_{gi} - C_{oi} = T^o_g\]

Denote the combined pose of rotation $R^o_g$ and translation $T^o_g$ as $G_o$, which can be thought of the pose of the Gazebo origin in the Optitrack frame. More intuitive notation might be $O_g$, the pose of the Optitrack marker in the Gazebo frame.

\subsection{Running}
Calculations at time $t$ when motion tracking is running:

$R_{\delta}$: pure rotational difference between $M_{gd}$ and $M_{gi}$.

\[M_{od} = M_{ot}\]
\[C_{od} = M_{ot} - (M_c + R_{\delta} + R^o_g)\]
\[C_{gd} = C_{od} + O_g\]

To implement the desired viewpoint effect in Gazebo, set the rotational component of the user camera to the rotational component of $C_{gi}$, and set the translational component of the user camera to the translational component of $C_{gd}$.

\end{document}
